Vulnerability Analysis of Container Images in Neuroimaging

### 2020-05-31 paper.tex
content change 1

%%%% Packages %%%%
\usepackage{siunitx}
\usepackage{algpseudocode} % Algorithmic environment
\usepackage{xspace}
\usepackage{csvsimple}
\usepackage{minted} % Used for JSON highlighting
\usepackage{datatool}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{caption}
\usepackage[justification=centering]{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{adjustbox}
\usepackage{makecell}
\usepackage{titlesec}
\usepackage[flushleft]{threeparttable}

@@

We scanned a total of 44 container images taken from the BIDS
apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}
frameworks, two containerization frameworks used in neuroscience to share
and re-use applications. Among the 27 BIDS apps \href{https://bids-apps.neuroimaging.io/apps/}
{(https://bids-apps.neuroimaging.io/apps/)} available at the time of
the study, we studied 26
unique Docker images as one wasn't available on DockerHub. Among the 49
Boutiques applications available at the time of the study, listed using
Boutiques \texttt{bosh search} command, 23 unique container images were
listed including 3 that couldn't be retrieved and 2 that were already
included in BIDS apps. The resulting 18 images included 12 Docker images
and 6 Singularity images.
\tristan{I rewrote this paragraph to focus it on the information of relevance for the reader. 
You could take it as an example for other sections of the paper.}

%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

Container image scanners can be broadly categorized into static and dynamic
scanners. In static scanning, the image vulnerabilities are extracted from
file and package lists \tristan{Does it really look into files, or only installed packages? Please check. The difference is important 
when software is installed without using the package manager.}, without deploying the image in a container. In
dynamic scanning however, a container is started from the image and
\tristan{... It is still unclear how dynamic scanning works. Your text
mentions ``running a container from the image and then scanning the dynamic
behavior of the image'' but in practice it should explain what is executed
in the image: the package manager? other scanning tools? Please clarify by
completing this sentence.}

@@

We performed scanning on 2019-09-25 and for our experiments, we used a Docker image that was 
latest updated i.e with the tag 2019-09-18. So it means that Clair Scanner's database was already
old by one week.

@@

\subsection{Linux Distributions and Vulnerability Databases}

\tristan{This section lacks a sentence to introduce context: why are you even talking about distributions? 
You should explain that scanners report vulnerabilities differently depending on the release type. 
Also, is there a similar scheme in CentOS? }

BIDS app and Boutiques images that we took for our experiments have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
distribution can have different releases. As images in our experiments mostly have
Ubuntu distribution, we can take this distribution as an example \tristan{of what?}. In the case of Ubuntu, release
can be of two types: Regular or Long Term Support (LTS).
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance (ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
data in vulnerability databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
exists in LTS.

Ubuntu has ended support for some releases such as 14.04 LTS,
17.04, and 17.10, which means they have reached EOL. However, Ubuntu is providing optional extended support for Ubuntu 14.04.
To use this extended support, users have to buy ESM release for Ubuntu 14.04.
The images in our experiments have Ubuntu 14.04 LTS so scanners should refer
to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for 
vulnerability data, it may lead to discrepancies in results.
Also, if ubuntu release with ended support is used in images, there are no chances of getting updates, hence
resulting in vulnerable images.

@@

\subsection{Image Update Process}

\tristan{since the next 3 sections are rather short, I would group them all 
as paragraphs under the same sub-section.}

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github} \tristan{link should point to the actual script, not the repo}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.

\subsection{Image size Reduction process}
If we want to reduce the number of vulnerabilities without effecting the reproducibility of the image,
image size reduction process is a good choice. In this process, we reduce the number of packages
installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
out which packages we need for the pipeline to function properly. Here, we use
Reprozip~\cite{rampin2016reprozip}. It is a tool that
is used to make applications reproducible. It traces operating system calls used by the
application while execution and then based on that it recognizes binaries, files, environment variables,
and library dependencies that will be used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, we get a list of packages from Reprozip that are needed for the application execution. 
After that, we expand this list by adding important and required packages that are essential
for the system to function and finally figure out all the dependencies of these packages using Debtree
~\cite{debtree}.
Ultimately, we keep these packages and remove remaining unnecessary packages. We use a bash script
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github} \tristan{Link is broken}) for
the image size reduction process, which installs Reprozip in the image, collects Reprozip trace, and
finally deletes unnecessary packages.

\tristan{You should explain why you didn't use Neurodocker as it's the obvious way to do this.}

\subsection{Update and Size Reduction Together}

Our final experiment involves a combination of both update and size reduction process
to lessen the number of vulnerabilities.
So in this process we first update all the packages in the image and then deletes
the unnecessary packages. For this process we used the same two scripts that
we used for earlier experiments.

\tristan{This could go to the first sentences of the new sub-section, no need for a subsection for that.}

@@

In this section,
we first discuss the existing vulnerabilities in the images and compare the
results of the three scanners. We then discuss the effect of the update on the
existing vulnerabilities followed by the results of the image size reduction
process. Lastly, this section presents the combined effect of update and image size reduction on the
vulnerabilities.
\tristan{Probably not really at random... 
No need to mention anything if it was completely arbitrary. You should mention that just in the experiments themselves, it's giving this comment too much importance to put it here.}.

@@

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased \tristan{mention the parameters of the regression line (preferably as a label in the figure) and the regression error}.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains the highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine \tristan{I dont think there is enough data to 
claim that, claim should be softened.}.
Similarly, Figure~\ref{sing} \tristan{there is a reference error, and if it's still a different figure I think you should make only 1.} illustrates the number of vulnerabilities in Singularity images used in Boutiques images.
\tristan{In the Figure, could you increase the marker size in the caption, and order it so that the different versions of a distribution 
are grouped together and sorted by increasing version?}
\begin{table*}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table*}
%\begin{comment}
%\begin{table}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c|c},
%	table head ={Image Tag} & {Image Name}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{names.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{\label{table2}Image names}
%\end{table}
%\end{comment}
\begin{figure}
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/vennDiagram.pdf}}
        \caption{\label{fig:venn} Scanner results}
\end{figure}

@@

\textbf{False negatives by Clair:} Clair is missing vulnerabilities that it should detect. For example, CVE-2016-9082 
is present in package Cairo in Xenial release and it is not detected by Clair. \tristan{You should report the version of Clair in 
the methods. If you reported this bug to the developers, you should say so and link it here (same comment for all the bugs).}

\textbf{False positives by Clair:} These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274.

@@

\textbf{Rejected CVEs:} There are some CVE that are rejected because they are duplicate copies of other CVEs. 
	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753.

\subsection{Effect Of Update}
%\begin{comment}
%The next experiment involves updating all these images and then rescanning them to see how the number of
%vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
%present in our Github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
%{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
%will find the package manager inside the image and then update the image according to the package manager it finds.
%\end{comment}

@@

\begin{figure*}
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/graphwithdeletedpackages.pdf}}
	\caption{\label{deleted}\#Deleted Packages vs \#Reduced Vulnerabilities}
\end{figure*}

@@

Our third experiment involves deleting unnecessary packages from the images.
We did this experiment only on five images because the reduction process takes
several hours.\tristan{This is not a good argument, it is vague, and it is not complete. Size reduction also requires 
to run a pipeline in the image.}. We selected these five images at random \tristan{really? I don't think so.}. We noticed that
after the size reduction process, the scanning results deviate a little from our initial belief \tristan{what do you mean?}.
At first, we thought that we will have a notable effect of size reduction on
vulnerabilities. However, this is not the case always. The bar graph shown in
Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
\textit{poldracklab/fmriprep:1.2.3} have an insignificant effect of size reduction.
According to our analyzes here, this can be due to two reasons: \rom{1}) the number
and \rom{2}) the kind of packages that we deleted. In other
words, if we delete a low number of packages then vulnerabilities do not get decreased as expected.
In contrast, if the number of deleted packages are high, reduction
in vulnerabilities also becomes high. For instance, we were able to delete only 21 and 25 packages for 
\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
reduced only by 4 and 17 respectively. Furthermore, this is illustrated in Figure~\ref{deleted} \tristan{I'm not thrilled by this figure, I would 
just mention in the text that we verified that.}.
\tristan{The next sentence is interesting because it starts characterizing the images that benefit the most 
from size reduction. The previous sentences read like a tautology, you should make your comment more specific.} 
Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
vulnerabilities by a significant number. For instance, in case of our experiments
deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}. 
%Our third experiment shows that deleting unnecessary packages from the image also helps to reduce
%the number of vulnerabilities by a significant number. We started this experiment with
%\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
%to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
%to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
%from 353 to 101.

>>>>

%%%% Packages %%%%
\usepackage{siunitx}
\usepackage{algpseudocode} % Algorithmic environment
\usepackage{xspace}
\usepackage{csvsimple}
\usepackage{minted} % Used for JSON highlighting
\usepackage{datatool}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{array}
\usepackage{algorithm}
\usepackage{caption}
\usepackage[justification=centering]{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{adjustbox}
\usepackage{makecell}
\usepackage{titlesec}
\usepackage[flushleft]{threeparttable}

@@

We scanned a total of 44 container images taken from the BIDS
apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}
frameworks, two containerization frameworks used in neuroscience to share
and re-use applications. Among the 27 BIDS apps \href{https://bids-apps.neuroimaging.io/apps/}
{(https://bids-apps.neuroimaging.io/apps/)} available at the time of
the study, we studied 26
unique Docker images as one wasn't available on DockerHub. Among the 49
Boutiques applications available at the time of the study, listed using
Boutiques \texttt{bosh search} command, 23 unique container images were
listed including 3 that couldn't be retrieved and 2 that were already
included in BIDS apps. The resulting 18 images included 12 Docker images
and 6 Singularity images.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

\change{Container image scanners can be broadly categorized into static and dynamic
scanners. Static scanning performs analysis on a image without running it
as a container. Therefore, commands cannot be executed to inquire installed packages}

\tristan{Does it really look into files, or only installed packages? Please check. The difference is important 
when software is installed without using the package manager.}, without deploying the image in a container. In
dynamic scanning however, a container is started from the image and
\tristan{... It is still unclear how dynamic scanning works. Your text
mentions ``running a container from the image and then scanning the dynamic
behavior of the image'' but in practice it should explain what is executed
in the image: the package manager? other scanning tools? Please clarify by
completing this sentence.}

@@

\change{In our experiments, we used a Docker image (arminc/clair-local-scan:v2.0.6) for scanning
and an another Docker image (arminc/clair-db:latest) for the vulnerability database, which was
last updated on 2019-09-18. We performed
scanning on 2019-09-25. So, it means that Clair Scanner's database was already
old by one week.}

@@

\begin{table*}
  \caption{some table}
	\begin{tabular}{>|{\bfseries}c| c| c| *{4}{c|}}\hline
	  \multirow{2}{*}{\bfseries Image Labels} & 
	  \multirow{2}{*}{\bfseries Image Names} & 
	  \multirow{2}{*}{\bfseries OS} & 
	  \multicolumn{4}{c|}{\bfseries Vulnerabilities} \\\cline{2-5} 
                       & \textbf{A} & \textbf{C} & \textbf{V}  & \textbf{S} \\ \hline
a	& bids/example	& ubuntu:14.04	& 838	& 663	& 683	& \\ \hline
b	& bids/freesurfer	& ubuntu:14.04	& 353	& 215	& 192	& \\ \hline
c	& bids/ndmg	& ubuntu:14.04	& 934	& 757	& 782	& \\ \hline
d	& bids/broccoli:v1.0.0	& centos 6	& 79	& 79	& 117	& \\ \hline
e	& bids/fibredensityandcrosssection	& ubuntu:14.04	& 1086	& 849	& 868	& \\ \hline
f	& bids/spm	& ubuntu:14.04	& 191	& 246	& 235	& \\ \hline
g	& poldracklab/mriqc:0.15.0	& ubuntu:16.04	& 432	& 328	& 332	& \\ \hline
h	& bids/cpac:v1.0.1a\_22	& ubuntu:16.04	& 698	& 524	& 535	& \\ \hline
I	& bids/hyperalignment	& ubuntu:16.04	& 1717	& 1327	& 1433	& \\ \hline
j	& bids/mindboggle:0.0.4-1	& debian:8	& 671	& 955	& 569	& \\ \hline
k	& bids/mrtrix3\_connectome	& ubuntu:18.04	& 275	& 157	& 158	& \\ \hline
l	& bids/rs\_signal\_extract:0.1	& ubuntu:16.04	& 867	& 454	& 473	& \\ \hline
m	& bids/aa:v0.2.0	& ubuntu:14.04	& 189	& 244	& 233	& \\ \hline
n	& bids/niak	& ubuntu:16.04	& 1482	& 1366	& 1420	& \\ \hline
o	& bids/oppni:v0.7.0-1	& ubuntu:14.04	& 913	& 698	& 723	& \\ \hline
p	& poldracklab/fmriprep:unstable	& ubuntu:16.04	& 516	& 355	& 393	& \\ \hline
q	& bids/brainiak-srm	& ubuntu:16.04	& 897	& 484	& 503	& \\ \hline
r	& bids/nipypelines:0.3.0	& debian:8	& 641	& 878	& 451	& \\ \hline
s	& bids/hcppipelines:v3.17.0-18	& debian:8	& 526	& 873	& 620	& \\ \hline
t	& bids/magetbrain	& ubuntu:18.04	& 112	& 117	& 126	& \\ \hline
u	& bids/tracula:v6.0.0-4	& ubuntu:14.04	& 874	& 664	& 683	& \\ \hline
v	& bids/baracus	& ubuntu:14.04	& 172	& 238	& 216	& \\ \hline
w	& bids/antscorticalthickness:v2.2.0-1	& ubuntu:17.04	& 289	& 27	& no oval data	& \\ \hline 
x	& bids/dparsf:v4.3.12	& ubuntu:14.04	& 507	& 750	& 757	& \\ \hline
y	& bids/afni\_proc	& ubuntu:17.10	& 67	& 16	& no oval data	& \\ \hline
z	& bids/rshrf:1.0.1	& alpine:3.8.4	& 5	& 3	& 3	& \\ \hline
aa	& bids/ndmg:v0.1.0	& ubuntu 14.04	& 934	& 758	& 782	& \\ \hline
ab	& mcin/qeeg:latest	& centos 7	& 46	& 46	& 142	& \\ \hline
ac	& camarasu/creaphase:0.3	& centos 7	& 54	& 54	& 186	& \\ \hline
ad	& bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest	& centos 7	& 70	& 76	& 157	& \\ \hline
ae	& mcin/docker-fsl:latest	& centos 7	& 75	& 75	& 201	& \\ \hline
af	& gkiar/onevoxel:v0.3.0rc2	& alpine 3.7.1	& 5	& 2	& 2	& \\ \hline
ag	& bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest	& centos 7	& 70	& 76	& 157	& \\ \hline 
ah	& bt5e/ants:latest	& centos 7	& 150	& 156	& 336	& \\ \hline
ai	& poldracklab/fmriprep:1.2.3	& ubuntu 16.04	& 591	& 441	& 447	& \\ \hline
aj	& gkiar/dwipreproc\_fsl-5.0.11\_minified	& ubuntu 16.04	& 391	& 258	& 263	& \\ \hline
ak	& gkiar/mask2boundary:v0.1.0	& alpine 3.9.0	& 15	& 11	& 11	& \\ \hline
al	& mcin/ica-aroma:latest	& centos 7	& 75	& 75	& 202	& \\ \hline
am	& c3genomics/genpipes	& 	& 	& 	& 	& 99 \\ \hline
an	& bioinformatics-group/aqua-singularity-recipe	& 	& 	& 	& 	& 7 \\ \hline
ao	& MontrealSergiy/BEst	& 	& 	& 	& 	& 106 \\ \hline
ap	& shub://aces/cbrain-containers-recipes:fsl\_v6.0.1	& 	& 	& 	& 	& 206 \\ \hline
aq	& shots47s/bids-freesurfer-6.0	& 	& 	& 	& 	& 212 \\ \hline
ar	& shots47s/bids-fmriprep-1.2.3	& 	& 	& 	& 	& 453 \\ \hline
  \end{tabular}
  \end{table*}

\subsection{Linux Releases and Vulnerability Databases}

\change{Image scanners report vulnerabilities differently depending on the Linux release types.
Therefore, we provide an overview of these Linux releases by taking an example. 
BIDS app and Boutiques images in our experiments have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
distribution have different releases in general. Here, we take Ubuntu as an example
to discuss different releases and their vulnerability databases. We took Ubuntu's example
because mostly images in our experiments have this distibution.} In the case of Ubuntu, release
can be of two types: Regular or Long Term Support (LTS).
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance (ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
data in vulnerability databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
exists in LTS.

For instance, Ubuntu has ended support for some releases such as 14.04 LTS,
17.04, and 17.10, which means they have reached EOL. However, Ubuntu is providing optional extended support for Ubuntu 14.04.
To use this extended support, users have to buy ESM release for Ubuntu 14.04.
The images in our experiments have Ubuntu 14.04 LTS so scanners should refer
to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for 
vulnerability data, it may lead to discrepancies in results.
Also, if ubuntu release with ended support is used in images, there are no chances of getting updates, hence
resulting in vulnerable images.

@@

\subsection{Image Update and Reduction Process}

\change{If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script 
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/update/update.sh}{Github}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.

On the other hand, if we want to reduce the number of vulnerabilities without effecting the reproducibility of the image,
image size reduction process is a good choice. The most obvious way of doing this is using 
Neurodocker (\href{https://github.com/ReproNim/neurodocker}{https://github.com/ReproNim/neurodocker}).
It traces and deletes unnecessary files.
However, image scanners reports vulnerabilities according to the installed
packages, whereas Neurodocker deals with the files only and list of installed packages remains same. Therefore, after
minimization also scanners report same number of vulnerabilities.
Hence, we need to reduce the number of packages
installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
out which packages we need for the pipeline to function properly. We use
Reprozip~\cite{rampin2016reprozip}, a tool that
is used to make applications reproducible. It traces operating system calls used by the
application while execution and then based on that it recognizes binaries, files, environment variables,
and library dependencies that will be used by the application for future re-execution. If the OS is
Debian or RPM-based, Reprozip also
uses an available package manager to acquire a list of distribution packages from where these files come from.
So, we get a list of packages from Reprozip that are needed for the application execution. 
After that, we expand this list by adding important and required packages that are essential
for the system to function and finally figure out all the dependencies of these packages using Debtree
~\cite{debtree}.
Ultimately, we keep these packages and remove remaining unnecessary packages. We use bash scripts
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{Github}) for
the image size reduction process, which installs Reprozip in the image, collects Reprozip trace, and
finally deletes unnecessary packages.

Finally, we combine both update and size reduction process
to lessen the number of vulnerabilities.
Therefore, in this process we first update all the packages in the image and then deletes
the unnecessary packages. For this process we used the same scripts that
we used for earlier experiments.}

@@

In this section,
we first discuss the existing vulnerabilities in the images and compare the
results of the three scanners. We then discuss the effect of the update on the
existing vulnerabilities followed by the results of the image size reduction
process. Lastly, this section presents the combined effect of update and image size reduction on the
vulnerabilities.

@@

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased \tristan{mention the parameters of the regression line (preferably as a label in the figure) and the regression error}.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains the highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine \tristan{I dont think there is enough data to 
claim that, claim should be softened.}.
Similarly, Figure~\ref{sing} \tristan{there is a reference error, and if it's still a different figure I think you should make only 1.} illustrates the number of vulnerabilities in Singularity images used in Boutiques images.
\tristan{In the Figure, could you increase the marker size in the caption, and order it so that the different versions of a distribution 
are grouped together and sorted by increasing version?}
\begin{table*}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table*}
%\begin{comment}
%\begin{table}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c|c},
%	table head ={Image Tag} & {Image Name}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{names.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{\label{table2}Image names}
%\end{table}
%\end{comment}
\begin{figure}
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/venn.pdf}}
        \caption{\label{fig:venn} Scanner results}
\end{figure}

@@

\textbf{False negatives by Clair:} Clair is missing vulnerabilities that it should detect. For example, CVE-2016-9082 
is present in package Cairo in Xenial release and it is not detected by Clair.

\textbf{False positives by Clair:} These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274. \change{The reasons of Clair showing
false positives and false negatives are unclear. We reported this issue on two Google groups of Clair i.e CoreOS Dev and
clair-dev (\href{https://groups.google.com/forum/#!topic/clair-dev/8IqCCfd-EEc}{https://groups.google.com/forum/#!topic/clair-dev/8IqCCfd-EEc}).
However, we did not receive any reply from developers.}

@@

\textbf{Rejected CVEs:} There are some CVE that are rejected because they are duplicate copies of other CVEs. 
	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753.
%\begin{table*}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\textwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c |c |c |c |c},
%	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls} & {a} & {b} & {c}\\\hline,
% late after line= \\,
%        late after last line=\\\hline
%]{status.csv}{}{\csvlinetotablerow}%
%       \centering
%        \caption{\label{status}Existing number of Vulnerabilities}
%\end{table*}
\subsection{Effect Of Update}
%\begin{comment}
%The next experiment involves updating all these images and then rescanning them to see how the number of
%vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
%present in our Github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
%{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
%will find the package manager inside the image and then update the image according to the package manager it finds.
%\end{comment}

@@

%\begin{figure*}
%        {\includegraphics[scale=1.5,width=\textwidth]
%        {Figures/graphwithdeletedpackages.pdf}}
%	\caption{\label{deleted}\#Deleted Packages vs \#Reduced Vulnerabilities}
%\end{figure*}

@@

Our third experiment involves deleting unnecessary packages from the images.
\change{We did this experiment on five images because the reduction process may take
several hours. Size reduction process also requires 
to run a pipeline in the image, which takes time}. We noticed that
after the size reduction process, the scanning results deviate a little from our initial expectation.
At first, we thought that we will have a notable effect of size reduction on
vulnerabilities. However, this is not the case always. The bar graph shown in
Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
\textit{poldracklab/fmriprep:1.2.3} have an insignificant effect of size reduction.
According to our analyzes here, this can be due to two reasons: \rom{1}) the number
and \rom{2}) the kind of packages that we deleted. In other
words, if we delete a low number of packages then vulnerabilities do not get decreased as expected.
In contrast, if the number of deleted packages are high, reduction
in vulnerabilities also becomes high. For instance, we were able to delete only 21 and 25 packages for 
\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
reduced only by 4 and 17 respectively. Furthermore, this is illustrated in Figure~\ref{deleted} \tristan{I'm not thrilled by this figure, I would 
just mention in the text that we verified that.}.
\tristan{The next sentence is interesting because it starts characterizing the images that benefit the most 
from size reduction. The previous sentences read like a tautology, you should make your comment more specific.} 
Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
vulnerabilities by a significant number. For instance, in case of our experiments
deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}. 
%Our third experiment shows that deleting unnecessary packages from the image also helps to reduce
%the number of vulnerabilities by a significant number. We started this experiment with
%\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
%to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
%to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
%from 353 to 101.
